Location of Marine fish - general Farms

### 2022-01-28 marine/last_step_rasterize/bivalve_rasterize_production.Rmd
updated for resubmission!

# CHN:HKG
# CHN:MAC
# CHN:PRK
# DEU:NLD
# HKG:CHN
# IRL:GBR
# MYS:BRN
# NLD:DEU
# SVN:HRV
# TWN:CHN
# USA:CAN

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:HKG", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:HKG", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:MAC", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:MAC", "China", NAME_0)) %>%
    mutate(GID_0 = ifelse(check %in% "CHN:PRK", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:PRK", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "DEU:NLD", "DEU", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "DEU:NLD", "Germany", NAME_0)) %>%    
  mutate(GID_0 = ifelse(check %in% "HKG:CHN", "HKG", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HKG:CHN", "Hong Kong", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "IRL:GBR", "IRL", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IRL:GBR", "Ireland", NAME_0)) %>% 
    mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:BRN", "Malaysia", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "NLD:DEU", "NLD", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "NLD:DEU", "Netherlands", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "SVN:HRV", "SVN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SVN:HRV", "Slovenia", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "TWN:CHN", "TWN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "TWN:CHN", "Taiwan", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "USA:CAN", "USA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "USA:CAN", "United States", NAME_0))

@@

cellStats(bivalve_raster, stat = "sum") # 17435623
sum(bivalve_raster_df$tonnes_production) # 17435623
sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 17435623
sum(fao$fao_tonnes_production) # 17435623

>>>>

# CHN:HKG
# CHN:MAC
# CHN:PRK
# CHN:TWN
# CHN:VNM
# HKG:CHN
# IRL:GBR
# KHM:VNM
# NLD:DEU
# SVN:HRV
# TWN:CHN
# USA:CAN

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:HKG", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:HKG", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:MAC", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:MAC", "China", NAME_0)) %>%
    mutate(GID_0 = ifelse(check %in% "CHN:PRK", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:PRK", "China", NAME_0)) %>%
      mutate(GID_0 = ifelse(check %in% "CHN:TWN", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:TWN", "China", NAME_0)) %>%
      mutate(GID_0 = ifelse(check %in% "CHN:VNM", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:VNM", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "HKG:CHN", "HKG", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HKG:CHN", "Hong Kong", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "IRL:GBR", "IRL", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IRL:GBR", "Ireland", NAME_0)) %>% 
    mutate(GID_0 = ifelse(check %in% "KHM:VNM", "KHM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "KHM:VNM", "Cambodia", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "NLD:DEU", "NLD", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "NLD:DEU", "Netherlands", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "SVN:HRV", "SVN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SVN:HRV", "Slovenia", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "TWN:CHN", "TWN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "TWN:CHN", "Taiwan", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "USA:CAN", "USA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "USA:CAN", "United States", NAME_0))

@@

cellStats(bivalve_raster, stat = "sum") # 17436803
sum(bivalve_raster_df$tonnes_production) # 17436803
sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 17436803
sum(fao$fao_tonnes_production) # 17435623 - slightly off?

### 2022-01-28 marine/last_step_rasterize/crustaceans_rasterize_production.Rmd
updated for resubmission!

sum(farms_sf$tonnes_per_farm) # 401719.1
sum(fao$fao_tonnes_production) # 401719.1

crustacean_raster_check <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum)
plot(log(crustacean_raster_check+1))
# s <- raster::select(crustacean_raster_check)
# plot(s)
cellStats(crustacean_raster_check, stat = "sum", na.rm = TRUE) # 401719.1

@@

cellStats(crustacean_raster, stat = "sum") # 401719.1
sum(crustacean_raster_df$tonnes_production) # 401719.1
sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 401719.1
sum(fao$fao_tonnes_production) # 401719.1

>>>>

sum(farms_sf$tonnes_per_farm) # 402573.6
sum(fao$fao_tonnes_production) # 401719.1

crustacean_raster_check <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum)
plot(log(crustacean_raster_check+1))
# s <- raster::select(crustacean_raster_check)
# plot(s)
cellStats(crustacean_raster_check, stat = "sum", na.rm = TRUE) # 402573.6

@@

cellStats(crustacean_raster, stat = "sum") # 402573.6
sum(crustacean_raster_df$tonnes_production) # 402573.6
sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 402573.6
sum(fao$fao_tonnes_production) # 401719.1

### 2022-01-28 marine/last_step_rasterize/finfish_rasterize_production.Rmd
updated for resubmission!

# CHN:HKG
# CHN:PRK
# CYP:XAD
# ESP:PRT
# GRC:ALB
# GRC:TUR
# HKG:CHN
# IDN:MYS
# MYS:BRN
# MYS:SGP
# SGP:MYS
# TWN:CHN

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:HKG", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:HKG", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:PRK", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:PRK", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CYP:XAD", "CYP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CYP:XAD", "Cyprus", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "ESP:PRT", "ESP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ESP:PRT", "Spain", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "GRC:ALB", "GRC", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "GRC:ALB", "Greece", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "GRC:TUR", "GRC", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "GRC:TUR", "Greece", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "HKG:CHN", "HKG", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HKG:CHN", "Hong Kong", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "IDN:MYS", "IDN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IDN:MYS", "Indonesia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:BRN", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "MYS:SGP", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:SGP", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "SGP:MYS", "SGP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SGP:MYS", "Singapore", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "TWN:CHN", "TWN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "TWN:CHN", "Taiwan", NAME_0))

@@

mapview(farms_sf_correct) # this all looks reasonable, no crazy points
```

@@

cellStats(finfish_raster, stat = "sum") # 3901214
sum(finfish_raster_df$tonnes_production) # 3901214
sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 3901214
sum(fao$fao_tonnes_production) #3901214

>>>>

# CHN:HKG
# CHN:PRK
# CHN:TWN
# CYP:XAD
# ESP:PRT
# GRC:ALB
# GRC:TUR
# HKG:CHN
# IDN:MYS
# MYS:SGP
# SGP:MYS

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:HKG", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:HKG", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:PRK", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:PRK", "China", NAME_0)) %>%
    mutate(GID_0 = ifelse(check %in% "CHN:TWN", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:TWN", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CYP:XAD", "CYP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CYP:XAD", "Cyprus", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "ESP:PRT", "ESP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "ESP:PRT", "Spain", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "GRC:ALB", "GRC", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "GRC:ALB", "Greece", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "GRC:TUR", "GRC", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "GRC:TUR", "Greece", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "HKG:CHN", "HKG", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HKG:CHN", "Hong Kong", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "IDN:MYS", "IDN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IDN:MYS", "Indonesia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "MYS:SGP", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:SGP", "Malaysia", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "SGP:MYS", "SGP", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SGP:MYS", "Singapore", NAME_0))

@@

@@

cellStats(finfish_raster, stat = "sum") # 3909255
sum(finfish_raster_df$tonnes_production) # 3909255
sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 3909255
sum(fao$fao_tonnes_production) #3901214

### 2022-01-28 marine/last_step_rasterize/salmon_rasterize_production.Rmd
updated for resubmission!

# CAN:USA
# FIN:ALA
# FIN:RUS
# USA:CAN

@@

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CAN:USA", "CAN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CAN:USA", "Canada", NAME_0)) %>%
  mutate(NAME_1 = ifelse(check %in% "CAN:USA", "New Brunswick", NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "USA:CAN", "USA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "USA:CAN", "United States", NAME_0)) %>%
  mutate(NAME_1 = ifelse(check %in% "USA:CAN", "Maine", NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "FIN:ALA", "FIN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "FIN:ALA", "Finland", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "FIN:RUS", "FIN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "FIN:RUS", "Finland", NAME_0))

@@

cellStats(salmon_raster, stat = "sum") # 2753752
sum(salmon_raster_df$tonnes_production) # 2753752
sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 2753752
sum(fao$fao_tonnes_production) #2753752

>>>>

# CAN:USA
# FIN:ALA
# FIN:RUS
# TUR:GRC
# USA:CAN

@@

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CAN:USA", "CAN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CAN:USA", "Canada", NAME_0)) %>%
  mutate(NAME_1 = ifelse(check %in% "CAN:USA", "New Brunswick", NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "USA:CAN", "USA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "USA:CAN", "United States", NAME_0)) %>%
  mutate(NAME_1 = ifelse(check %in% "USA:CAN", "Maine", NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "FIN:ALA", "FIN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "FIN:ALA", "Finland", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "FIN:RUS", "FIN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "FIN:RUS", "Finland", NAME_0))  %>%
    mutate(GID_0 = ifelse(check %in% "TUR:GRC", "TUR", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "TUR:GRC", "Turkey", NAME_0))

@@

cellStats(salmon_raster, stat = "sum") # 2756155
sum(salmon_raster_df$tonnes_production) # 2756155
sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 2756155
sum(fao$fao_tonnes_production) #2753752

### 2022-01-28 marine/last_step_rasterize/shrimp_rasterize_production.Rmd
updated for resubmission!

# CHN:HKG
# CHN:MAC
# CHN:PRK
# CRI:PAN
# HND:NIC
# HND:SLV
# IRN:IRQ
# MEX:USA
# MYS:BRN
# MYS:SGP
# PAN:CRI
# SAU:KWT
# SLV:GTM
# TWN:CHN

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:HKG", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:HKG", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:MAC", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:MAC", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:PRK", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:PRK", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CRI:PAN", "CRI", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CRI:PAN", "Costa Rica", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "HND:NIC", "HND", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HND:NIC", "Honduras", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "HND:SLV", "HND", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HND:SLV", "Honduras", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "IRN:IRQ", "IRN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IRN:IRQ", "Iran", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "MEX:USA", "MEX", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MEX:USA", "Mexico", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:BRN", "Malaysia", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "MYS:SGP", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:SGP", "Malaysia", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "PAN:CRI", "PAN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "PAN:CRI", "Panama", NAME_0)) %>%    
  mutate(GID_0 = ifelse(check %in% "SAU:KWT", "SAU", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SAU:KWT", "Saudi Arabia", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "SLV:GTM", "SLV", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SLV:GTM", "El Salvador", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "TWN:CHN", "TWN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "TWN:CHN", "Taiwan", NAME_0))

@@

cellStats(shrimp_raster, stat = "sum") # 5094133
sum(shrimp_raster_df$tonnes_production) # 5094133
sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 5094133
sum(fao$fao_tonnes_production) # 5094133

>>>>

# CHN:HKG
# CHN:PRK
# CHN:VNM
# CRI:PAN
# HND:NIC
# HND:SLV
# IDN:MYS 
# IRN:IRQ
# KHM:VNM 
# MEX:USA
# MYS:BRN
# MYS:SGP
# PAN:CRI
# SAU:KWT
# SLV:GTM
# THA:MYS -

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:HKG", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:HKG", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:VNM", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:VNM", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:PRK", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:PRK", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CRI:PAN", "CRI", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CRI:PAN", "Costa Rica", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "HND:NIC", "HND", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HND:NIC", "Honduras", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "HND:SLV", "HND", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HND:SLV", "Honduras", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "IRN:IRQ", "IRN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IRN:IRQ", "Iran", NAME_0)) %>%  
    mutate(GID_0 = ifelse(check %in% "IDN:MYS", "IDN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IDN:MYS", "Indonesia", NAME_0)) %>%  
      mutate(GID_0 = ifelse(check %in% "KHM:VNM", "KHM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "KHM:VNM", "Cambodia", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "MEX:USA", "MEX", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MEX:USA", "Mexico", NAME_0)) %>% 
  mutate(GID_0 = ifelse(check %in% "MYS:BRN", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:BRN", "Malaysia", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "MYS:SGP", "MYS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MYS:SGP", "Malaysia", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "PAN:CRI", "PAN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "PAN:CRI", "Panama", NAME_0)) %>%    
  mutate(GID_0 = ifelse(check %in% "SAU:KWT", "SAU", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SAU:KWT", "Saudi Arabia", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "SLV:GTM", "SLV", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SLV:GTM", "El Salvador", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "THA:MYS", "THA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "THA:MYS", "Thailand", NAME_0))

@@

cellStats(shrimp_raster, stat = "sum") # 5097823
sum(shrimp_raster_df$tonnes_production) # 5097823
sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 5097823
sum(fao$fao_tonnes_production) # 5094133 - a bit off bc of rounding with our model

### 2022-01-28 marine/marine_fish_general/finfish_farms/STEP2_finfish_farm_locations.Rmd
updated figs and stats with newly run farms
updated for resubmission!

ASC_finfish <- ASC_data %>%
  dplyr::filter(aq_grop == "marine_fish_general")

@@

## China 
Can't find any datasets of marine finfish farm locations in China. This will need to be fully gapfilled.

```{r}
chn_gf <- data.frame(iso3c = "CHN", type = "marine_fish_general", num_additional_farms = NA, data_quality = 1)
write_csv(chn_gf, here("marine/marine_fish_general/finfish_farms/data/no_info_1/gf_chn.csv"))

>>>>

ASC_finfish <- ASC_data %>%
  dplyr::filter(aq_grop == "marine_fish_general")
mapview(ASC_finfish)

@@

## China

Current data is from https://zenodo.org/record/3881612 only 459 farms, so probably not comprehensive, just a drop in the bucket compared to the produciton of China. There are likely many more farms than this. Because we can't find any information on more specific locations or specific number of farms, we will gapfill later based on global tonnes/farm. For now we need to mark the data quality as 2.

```{r}
# chn_gf <- data.frame(iso3c = "CHN", type = "marine_fish_general", num_additional_farms = NA, data_quality = 1)
# write_csv(chn_gf, here("marine/marine_fish_general/finfish_farms/data/no_info_1/gf_chn.csv"))

farms_chn <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/China/split_spp/farms_mfg_chn.csv") %>%
  dplyr::select(-id) %>%
  mutate(data_quality = 2)

write_csv(farms_chn, here("marine/marine_fish_general/finfish_farms/data/known_farm_sites_2_4_5/farms_chn.csv"))
